О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
Kurz's estimate of the diameter for sets with many collinear points

In [TODO:cite], TODO: theorem about sublinear quantity of points on the line.
However, we need the values of all the constants in such an estimate.
To obtain such values, we will now prove a generalization of~\cite[lemma 3]{our-vmmsh-2018}.

>>>>

Now we need to estimate the quanity of points in an intersection of an integral point set and a line segment.
There is the following estimate for minimum diameter of planar integral point sets with many collinear points:
\begin{theorem}~\cite[Theorem 4]{kurz2008minimum}
	For $\delta > 0$, $\varepsilon > 0$, and $P\in\mathfrak{M}(2,n)$ with
	at least $n^\delta$ collinear points there exists a $n_0 (\varepsilon)$
	such that for all $n \geq n_0 (\varepsilon)$ we have
	\begin{equation}
		\operatorname{diam} P \geq n^{\frac{\delta}{4 log 2(1+\varepsilon)}\log \log n}
		.
	\end{equation}
\end{theorem}
However, the estimate is rather unsuitable for our needs,
as it does not provide the values of all the constants.
To obtain the desired estimate, we will now prove a generalization of~\cite[lemma 3]{our-vmmsh-2018}.
